|

### 2023-01-23 paper_comparison/paper_comparison/paper_comparison.Rmd
fix plot caption

```{r first-example-lineup, fig.height = 7, fig.cap="Visual testing is conducted using a lineup, as in the example here. The residual plot computed from the observed data (plot $2^2 + 2$, exhibiting non-linearity) is embedded among 19 null plots, where the residuals are simulated from a standard error model. Computing the $p$-value requires that the lineup be examined by a number of human judges, each asked to select the most different plot. A small $p$-value would result from a substantial number selecting plot $2^2 + 2$."}

@@

\noindent where $diag(.)$ is the diagonal matrix constructed from the diagonal elements of a matrix,  $\boldsymbol{X}_a = (\boldsymbol{1},  \boldsymbol{X})$ is the matrix of regressors including the intercept used in the regression equation, $\sigma^2$ is the assumed variance of the error term when $H_0$ is true, $\boldsymbol{V}$ is the actual variance of the error term, and $\boldsymbol{\mu}_z = \boldsymbol{R}_a\boldsymbol{Z}\boldsymbol{\beta}_z$ is the expected values of the residuals with $\boldsymbol{Z}$ be any variables leave out by the model and $\boldsymbol{\beta}_z$ be the corresponding coefficients.

To study various factors contributing to the power of the visual test, the same logistic regression model is fit on different subsets of the collated data grouped by levels of factors. These include the distribution of the regressor and the type of the simulated model (modify this according to the result).

@@

```{r different-shape-of-herimite, fig.height = 2, fig.cap="Polynomial forms generated for the residual plots used in experiment I. The four shapes are generated by varying the order of polynomial given by $j$ in $He_j(.)$."}

@@

```{r different-dist, fig.height = 2, fig.cap="Variations in fitted values, that might affect perception of residual plots. Four different distribution are used."}

@@

Figure \ref{fig:example-poly-lineup} demonstrates one of the lineups used in experiment I. This lineup is produced by the non-linearity model under $j = 6$ and fitted values follow a uniform distribution. The data plot location is $2^3 - 4$. All five subjects correctly identify the data plot from this lineup.

```{r different-n, fig.height = 2.67, fig.cap="Three different values of $n$ are used in experiment I, II and III to control the strength of the signal."}

@@

```{r different-sigma, fig.height = 2, fig.cap="Four different values of $\\sigma$ are used in the experiment I to control the strength of the signal."}

@@

```{r example-poly-lineup, fig.height = 7, fig.cap="Lineup poly-24 in experiment I. Can you spot the most different plot? \\label{fig:example-poly-lineup}"}
VI_MODEL$plot_lineup(vi_lineup$poly_24$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r different-shape-of-heter, fig.height = 2.67, fig.cap="Heteroskedasticity forms used in experiment II. Three different shapes (a = -1, 0, 1) are used in the experiment to create left-triangle, butterfly and right-triangle shapes."}

@@

```{r different-b, fig.height = 2, fig.cap="Five different values of $b$ are used in experiment II to control the strength of the signal."}

@@

```{r example-heter-lineup, fig.height = 7, fig.cap="Lineup heter-169 in experiment II. Can you spot the most different plot? \\label{fig:example-heter-lineup}"}

@@

All lineups consist of only null plots are planned to be evaluated by 20 subjects. 
However, presenting only these lineups to subjects are considered to be bad practices as subjects will lose interest quickly. 
Therefore, we plan to collect 6 more evaluations on the 279 lineups with fitted values follow a uniform distribution, result in $(36 \times 20 + (4 \times 4 \times 3 + 3 \times 5 \times 3) \times 3 \times 6) / (20-2) = `r (36 * 20 + (4 * 4 * 3 + 3 * 5 * 3) * 3 * 6) / 18`$ subjects recruited for experiment III.

@@

In the following analysis, lineups with fitted values follows a uniform distribution will be the focus of next two sections. Visual patterns are more likely to be revealed under a uniform distribution. Additionally, we have collected extra evaluations on these lineups, which will result in more reliable analysis. Analysis of lineups with other fitted value distributions can be found in Section \ref{fitted-value-distribution}.

@@

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with fitted values follow a uniform distribution, against the natural logarithm of the effect $log_e(E)$, with a 5% significance level. At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residual plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes detectable.

@@

For the non-linearity model, the power curve of RESET test climbs aggressively from
`r round(unname(predict(conv_poly_glmmod, newdata = data.frame(log_effect_size = 0), type = "response")) * 100)`% to `r round(unname(predict(conv_poly_glmmod, newdata = data.frame(log_effect_size = 2), type = "response")) * 100)`% as $log_e(E)$ increases from 0 to 2, while power of other tests respond inactively to the change of effect, showing that RESET test is way more sensitive to the type of model defects that being considered. Meanwhile, no noticeable visual features can be spotted from the example residual plots.

In terms of the heteroskedasticity model, the power of Breusch-Pagan test is also almost always greater than the power of visual test. For $0 \leq log_e(E) \leq 2$, where the power curve of the visual test remains at a low level, the Breusch-Pagan test still have a decent amount of chance of rejecting $H_0$. Similarly, the visual feature is nearly unobservable from the example residual plots.

The power of visual test arises steadily as $log_e(E)$ increases from 2 to 5 for both non-linearity model and heteroskedasticity model, suggesting that the effect starts to make significant impact on the degree of the presence of the designed visual features. This can also be observed from the example residual plots that when $log_e(E) = 2.5$, a weak "S-shape" and a weak "triangle" shape are presented in Figure \ref{fig:polypower} and Figure \ref{fig:heterpower} respectively. The visual pattern becomes much clearer as $log_e(E)$ increases. At $log_e(E) \approx 6$, the power reaches almost 100%.

@@

```{r polypower, fig.height = 3, fig.width = 5, fig.cap="Comparison of power between different tests for non-linear patterns (uniform fitted values only). Main plot shows the power curves estimated using logistic regression, with dots indicating human evaluations of lineups. Surrounding curves of the visual test show 500 samples of bootstrap estimation.  Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 1.5, but for the visual test it is around 3.5."}

@@

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap="Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating human evaluations of lineups. Surrounding curves of the visual test show 500 samples of bootstrap estimation. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 1.5, but for the visual test it is around 3."}

@@

```{r p-value-comparison, fig.width = 8, fig.height = 4, fig.cap="Rejection rate ($p$-value $<0.05$) of visual test conditional on the conventional test decision on non-linearity (left) and heteroskedasticity (right) lineups (uniform fitted values only) displayed using a mosaic plot. The visual test rejects less frequently than the conventional test. We would generally expect that the visual test would only reject when the conventional test does. Surprisingly, there is one lineup in the heteroskedasticity study where this is not the case. "}

@@

Figure \ref{fig:p-value-comparison} provides a mosaic plot showing the rejection rate of visual tests and conventional tests for both the non-linearity model and the heteroskedasticity model.

For lineups produced by the non-linearity model, conventional tests reject `r p_value_cmp_dat %>% filter(type == "non-linearity") %>% count(conv_reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% 
and visual tests reject `r p_value_cmp_dat %>% filter(type == "non-linearity") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% of the time. Of the tests rejected by the conventional test, `r p_value_cmp_dat %>% filter(type == "non-linearity") %>% filter(conv_reject == "Reject") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by the visual test, that is, approximately half as many as the conventional test. There are no lineups that are rejected by the visual test but not by the conventional test.

@@

For lineups produced by the non-linearity model, conventional tests reject `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(conv_reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% 
and visual tests reject `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% of the time. Of the tests rejected by the conventional test, `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% filter(conv_reject == "Reject") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by the visual test, that is, approximately half as many as the conventional test.

@@

```{r heter-example, fig.height = 7, fig.cap = 'The single heteroskedasticity lineup that is rejected by the visual test but not by the BP test. The data plot at panel 17 contains a "Butterfly" shape. It has effect size$ = 4.02$, somewhat surprising that it is not detected by the BP test.'}
# plot heter-331
VI_MODEL$plot_lineup(vi_lineup$heter_331$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

## Effect of other factors used in the simulated model

@@

For the non-linearity model, we do not observe significant difference in power of visual test between distributions, except for the discrete uniform distribution. It is possibility due to the fact that humans have difficulties in recognising visual patterns from discreteness, which makes the shape disconnected and incomplete (ref?). In terms of conventional tests, the discrete uniform distribution is instead the one with the greatest power, followed by the lognormal distribution, the uniform distribution and the normal distribution.

For the heteroskedasticity model, the power of visual test on lineups with uniform distribution has the greatest power. This is as expected since other three distributions could reduce the chance of revealing the underlying visual pattern because of uneven data points. Although the power of visual test under the discrete uniform  distribution is the lowest in the case of non-linearity model, it has a relatively great power this time. Considering for heteroskedasticity, the visual patterns are usually detected by connecting the maximum and minimum residuals separately at different fitted values. It will not be greatly affected by the discrete uniform distribution compared to the uniform distribution. Visual tests have low power on lineups with the normal distribution and the lognormal distribution. This suggests the use of transformation of fitted values in reading residual plots. In the case of conventional tests, the discrete uniform distribution consistently doing great, followed by the uniform distribution, the normal distribution and the lognormal distribution.

In regards of the type of the simulated model, the power of visual tests under different distributions of regressor are always lower than the corresponding conventional tests, which is consistent with the result from the previous sections.

```{r different-x-dist-poly-power, fig.height = 4, fig.cap = "Power of conventional tests and visual tests on lineups produced by the non-linearity model under different fitted value distributions."}

@@

@@

```{r p-value-comparison-old, eval = FALSE, fig.height = 4, fig.cap="Visual test p-value compared to conventional test p-value for lineups produced by heteroskedasticity and non-linearity model. The scatter plot is drawn on a square root scale. Every dot on the plot corresponds to a lineup. Most of the dots are fallen on the left of the y = x line indicating visual test p-value is almost always higher than conventional test p-value. The blue curve is a smoothing of the dots showing a positive trend. "}
vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  left_join(vi_survey %>% 
           count(unique_lineup_id) %>%
           rename(num_subject = n)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  ggplot() +
  geom_abline() +
  geom_point(aes(conventional_p_value, p_value), alpha = 0.4) +
  geom_smooth(aes(conventional_p_value, p_value), se = FALSE, span = 0.6) +
  scale_x_sqrt() +
  scale_y_sqrt() +
  facet_wrap(~type) +
  ylab("Visual test p-value on square root scale") +
  xlab("Conventional test p-value on square root scale") +
  theme_light()
```

>>>>

```{r first-example-lineup, fig.height = 7, fig.cap = "Visual testing is conducted using a lineup, as in the example here. The residual plot computed from the observed data (plot $2^2 + 2$, exhibiting non-linearity) is embedded among 19 null plots, where the residuals are simulated from a standard error model. Computing the $p$-value requires that the lineup be examined by a number of human judges, each asked to select the most different plot. A small $p$-value would result from a substantial number selecting plot $2^2 + 2$."}

@@

\noindent where $diag(.)$ is the diagonal matrix constructed from the diagonal elements of a matrix,  $\boldsymbol{X}_a = (\boldsymbol{1},  \boldsymbol{X})$ is the matrix of regressors including the intercept used in the regression equation, $\sigma^2\boldsymbol{I}$ is the assumed variance of the error term when $H_0$ is true, $\boldsymbol{V}$ is the actual variance of the error term, and $\boldsymbol{\mu}_z = \boldsymbol{R}_a\boldsymbol{Z}\boldsymbol{\beta}_z$ is the expected values of the residuals with $\boldsymbol{Z}$ be any variables leave out by the model and $\boldsymbol{\beta}_z$ be the corresponding coefficients.

To study various factors contributing to the power of the visual test, the same logistic regression model is fit on different subsets of the collated data grouped by levels of factors. These include the distribution of the regressor and the type of the simulation model (modify this according to the result).

@@

```{r different-shape-of-herimite, fig.height = 2, fig.cap = "Polynomial forms generated for the residual plots used in experiment I. The four shapes are generated by varying the order of polynomial given by $j$ in $He_j(.)$."}

@@

```{r different-dist, fig.height = 2, fig.cap = "Variations in fitted values, that might affect perception of residual plots. Four different distributions are used."}

@@

Figure \ref{fig:example-poly-lineup} demonstrates one of the lineups used in experiment I. This lineup is produced by the non-linearity model with $j = 6$ and uniform fitted values. The data plot location is $2^3 - 4$. All five subjects correctly identify the data plot from this lineup.

```{r different-n, fig.height = 2.67, fig.cap = "Number of observations $n$ have an impact on the strength of the signal. Three different values of $n$ are used in experiment I, II and III."}

@@

```{r different-sigma, fig.height = 2, fig.cap = "For the non-lienearity model, the standard deviation of the error term $\\sigma$ affects the strength of the signal. Four different values of $\\sigma$ are used in the experiment I."}

@@

```{r example-poly-lineup, fig.height = 7, fig.cap = "One of the lineups containing non-linearity patterns used in experiment I. Can you spot the most different plot? The data plot is positioned at $2^3 + 1$."}
VI_MODEL$plot_lineup(vi_lineup$poly_24$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r different-shape-of-heter, fig.height = 2.67, fig.cap = "Heteroskedasticity forms used in experiment II. Three different shapes (a = -1, 0, 1) are used in the experiment to create left-triangle, butterfly and right-triangle shapes."}

@@

```{r different-b, fig.height = 2, fig.cap = "Five different values of $b$ are used in experiment II to control the strength of the signal."}

@@

```{r example-heter-lineup, fig.height = 7, fig.cap = "One of the lineups containing heteroskedasticity pattern used in experiment II. Can you spot the most different plot? The data plot is positioned at $3^3 - 3^2$"}

@@

All lineups consist of only null plots are planned to be evaluated by 20 subjects. 
However, presenting only these lineups to subjects are considered to be bad practices as subjects will lose interest quickly. 
Therefore, we plan to collect 6 more evaluations on the 279 lineups with uniform fitted values, result in $(36 \times 20 + (4 \times 4 \times 3 + 3 \times 5 \times 3) \times 3 \times 6) / (20-2) = `r (36 * 20 + (4 * 4 * 3 + 3 * 5 * 3) * 3 * 6) / 18`$ subjects recruited for experiment III.

@@

In the following analysis, lineups with uniform fitted values will be the focus of next two sections. Visual patterns are more likely to be revealed under a uniform distribution. Additionally, we have collected extra evaluations on these lineups, which will result in more reliable analysis. Analysis of lineups with other fitted value distributions can be found in Section \ref{fitted-value-distribution}.

@@

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with uniform fitted values, against the natural logarithm of the effect $log_e(E)$, with a 5% significance level. At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residual plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes detectable.

@@

For non-linearity patterns, the power curve of RESET test climbs aggressively from
`r round(unname(predict(conv_poly_glmmod, newdata = data.frame(log_effect_size = 0), type = "response")) * 100)`% to `r round(unname(predict(conv_poly_glmmod, newdata = data.frame(log_effect_size = 2), type = "response")) * 100)`% as $log_e(E)$ increases from 0 to 2, while power of other tests respond inactively to the change of effect, showing that RESET test is way more sensitive to the type of model defects that being considered. Meanwhile, no noticeable visual features can be spotted from the example residual plots.

In terms of heteroskedasticity patterns, the power of Breusch-Pagan test is also almost always greater than the power of visual test. For $0 \leq log_e(E) \leq 2$, where the power curve of the visual test remains at a low level, the Breusch-Pagan test still have a decent amount of chance of rejecting $H_0$. Similarly, the visual feature is nearly unobservable from the example residual plots.

The power of visual test arises steadily as $log_e(E)$ increases from 2 to 5 for both non-linearity patterns and heteroskedasticity patterns, suggesting that the effect starts to make significant impact on the degree of the presence of the designed visual features. This can also be observed from the example residual plots that when $log_e(E) = 2.5$, a weak "S-shape" and a weak "triangle" shape are presented in Figure \ref{fig:polypower} and Figure \ref{fig:heterpower} respectively. The visual pattern becomes much clearer as $log_e(E)$ increases. At $log_e(E) \approx 6$, the power reaches almost 100%.

@@

```{r polypower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for non-linear patterns (uniform fitted values only). Main plot shows the power curves estimated using logistic regression, with dots indicating human evaluations of lineups. Surrounding curves of the visual test show 500 samples of bootstrap estimation.  Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 1.5, but for the visual test it is around 3.5."}

@@

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating human evaluations of lineups. Surrounding curves of the visual test show 500 samples of bootstrap estimation. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 1.5, but for the visual test it is around 3."}

@@

```{r p-value-comparison, fig.width = 8, fig.height = 4, fig.cap = "Rejection rate ($p$-value $<0.05$) of visual test conditional on the conventional test decision on non-linearity (left) and heteroskedasticity (right) lineups (uniform fitted values only) displayed using a mosaic plot. The visual test rejects less frequently than the conventional test. We would generally expect that the visual test would only reject when the conventional test does. Surprisingly, there is one lineup in the heteroskedasticity study where this is not the case. "}

@@

Figure \ref{fig:p-value-comparison} provides a mosaic plot showing the rejection rate of visual tests and conventional tests for both non-linearity patterns and heteroskedasticity patterns.

For lineups containing non-linearity patterns, conventional tests reject `r p_value_cmp_dat %>% filter(type == "non-linearity") %>% count(conv_reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% 
and visual tests reject `r p_value_cmp_dat %>% filter(type == "non-linearity") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% of the time. Of the tests rejected by the conventional test, `r p_value_cmp_dat %>% filter(type == "non-linearity") %>% filter(conv_reject == "Reject") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by the visual test, that is, approximately half as many as the conventional test. There are no lineups that are rejected by the visual test but not by the conventional test.

@@

For lineups containing non-linearity patterns, conventional tests reject `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(conv_reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% 
and visual tests reject `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% of the time. Of the tests rejected by the conventional test, `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% filter(conv_reject == "Reject") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by the visual test, that is, approximately half as many as the conventional test.

@@

```{r heter-example, fig.height = 7, fig.cap = 'The single heteroskedasticity lineup that is rejected by the visual test but not by the BP test. The data plot at panel 17 contains a "Butterfly" shape. It has effect size $ = 4.02$, somewhat surprising that it is not detected by the BP test.'}
# plot heter-331
VI_MODEL$plot_lineup(vi_lineup$heter_331$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

## Effect of other factors used in the simulation model

@@

For non-linearity patterns, we do not observe significant difference in power of visual test between distributions, except for the discrete uniform distribution. It is possibility due to the fact that humans have difficulties in recognising visual patterns from discreteness, which makes the shape disconnected and incomplete (ref?). In terms of conventional tests, the discrete uniform distribution is instead the one with the greatest power, followed by the lognormal distribution, the uniform distribution and the normal distribution.

For heteroskedasticity patterns, the power of visual test on lineups with uniform distribution has the greatest power. This is as expected since other three distributions could reduce the chance of revealing the underlying visual pattern because of uneven data points. Although the power of visual test under the discrete uniform distribution is the lowest in the case of non-linearity patterns, it has a relatively great power this time. Considering for heteroskedasticity, the visual patterns are usually detected by connecting the maximum and minimum residuals separately at different fitted values. It will not be greatly affected by the discrete uniform distribution compared to the uniform distribution. Visual tests have low power on lineups with the normal distribution and the lognormal distribution. This suggests the use of transformation of fitted values in reading residual plots. In the case of conventional tests, the discrete uniform distribution consistently doing great, followed by the uniform distribution, the normal distribution and the lognormal distribution.

In regards of the type of the simulation model, the power of visual tests under different fitted value distributions are always lower than the corresponding conventional tests, which is consistent with the result reported in the previous sections.

```{r different-x-dist-poly-power, fig.height = 4, fig.cap = "Comparison of power of conventional tests and visual tests on lineups produced by the non-linearity model under different fitted value distributions."}

@@

Shape of the non-linearity pattern is another factor contributed to the simulation model.

@@

```{r p-value-comparison-old, eval = FALSE, fig.height = 4, fig.cap = "Visual test p-value compared to conventional test p-value for lineups produced by heteroskedasticity and non-linearity model. The scatter plot is drawn on a square root scale. Every dot on the plot corresponds to a lineup. Most of the dots are fallen on the left of the y = x line indicating visual test p-value is almost always higher than conventional test p-value. The blue curve is a smoothing of the dots showing a positive trend. "}
vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  left_join(vi_survey %>% 
           count(unique_lineup_id) %>%
           rename(num_subject = n)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  ggplot() +
  geom_abline() +
  geom_point(aes(conventional_p_value, p_value), alpha = 0.4) +
  geom_smooth(aes(conventional_p_value, p_value), se = FALSE, span = 0.6) +
  scale_x_sqrt() +
  scale_y_sqrt() +
  facet_wrap(~type) +
  ylab("Visual test p-value on square root scale") +
  xlab("Conventional test p-value on square root scale") +
  theme_light()
```
